### 2024-07-11 analysis/analysis.qmd
working on preprocessing and analysis

# select regression studies with r2
tmp <- dplyr::filter(R_summary,dimension=="valence")
tmp <- dplyr::filter(R_studies,dimension=="valence")
tmp<-drop_na(tmp)
#sqrt(tmp$values) # convert from R^2 to r
#tmp$stimulus_n <- 100 # ad-hoc for now

m.cor <- metacor(cor = values, 
                 n = stimulus_n,
                 studlab = unique_id,
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")

print(m.cor)
```

@@

```{r}
forest(m.cor,
       sortvar = TE,
       prediction = FALSE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "g", "SE"),studlab = citekey)
plot(eggers.test(m.cor))
```

@@

```
#### Re-run the analysis without the outliers

@@

fp = ggplot(aes(x = SE, y = Zr), data = tmpdata) +
  geom_point(shape = 1) +
  xlab('Standard Error') + ylab('Zr')+
  geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) +
  geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
   geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
  geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
#Reverse the x-axis ordering (se) so that the tip of the funnel will appear
#at the top of the figure once we swap the x- and y-axes...
  scale_x_reverse(breaks=seq(0,0.2,0.05),limits=c(0.2,0))+
#Specify the range and interval for the tick-marks of the y-axis (Zr);
#Choose values that work for you based on your data
  scale_y_continuous(breaks=seq(0.3,1.25,0.25),limits=c(0.3,1.25))+
#  scale_x_continuous(breaks=seq(0.2,0,0.05))+
#And now we flip the axes so that SE is on y- and Zr is on x-
  coord_flip()+
#Finally, apply my APA-format theme (see code at end of post).
#You could, alternatively, specify theme_bw() instead.
  theme_bw()

@@

# select regression studies with r2
tmp <- dplyr::filter(R_summary,dimension=="arousal")
m.cor <- metacor(cor = valuesMedian, 
                 n = stimulus_n,
                 studlab = studyREF,
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Arousal: Summary")

print(m.cor)
```

>>>>

# select regression studies with r2
tmp <- dplyr::filter(R_summary,dimension=="valence")
tmp <- dplyr::filter(R_studies,dimension=="valence")
dim(tmp)
tmp <- tmp[!is.na(tmp$values),]
dim(tmp)

#sqrt(tmp$values) # convert from R^2 to r
#tmp$stimulus_n <- 100 # ad-hoc for now

m.cor <- metacor(cor = values,     # values 
                 n = stimulus_n,
                 studlab = unique_id, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 backtransf = TRUE,
                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")

#print(m.cor)

m.cor_backtransformed <- m.cor
m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
print(funnel(m.cor_backtransformed, common = FALSE, studlab=TRUE,backtransf=TRUE))

```
#### Custom plot

```{r}
tmpdata <- data.frame(SE = FisherZInv(m.cor$seTE), Zr = FisherZInv(m.cor$TE),studies=m.cor$studlab)

tmpdata$citekey<-str_replace_all(tmpdata$studies,'-.*$','')
tmpdata$citekey<-factor(tmpdata$citekey)

g <- ggplot(tmpdata,aes(y = SE, x = Zr,label=studies,color=citekey,fill=citekey)) +
  geom_point(show.legend = FALSE) +
  geom_label_repel(size=1.5,max.overlaps = 39,color="black",show.legend = FALSE)+
  ylab('Standard Error') + 
  xlab('r')+
  scale_y_reverse()+
  scale_x_continuous(breaks=seq(0.0,1.0,0.25),limits=c(0,1.0))+
#  coord_flip()+
  theme_bw()
print(g)
```

@@

```{r}
forest(m.cor,
       sortvar = TE,
       prediction = FALSE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "g", "SE"),studlab = citekey)

funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)

@@

#### Re-run the analysis without the outliers

@@

fp = ggplot(aes(x = SE, y = Zr), data = tmpdata) +
  geom_point(shape = 1) +
  xlab('Standard Error') + ylab('Zr')+
  geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) +
  geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
   geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
  geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
#Reverse the x-axis ordering (se) so that the tip of the funnel will appear
#at the top of the figure once we swap the x- and y-axes...
  scale_x_reverse(breaks=seq(0,0.2,0.05),limits=c(0.2,0))+
#Specify the range and interval for the tick-marks of the y-axis (Zr);
#Choose values that work for you based on your data
  scale_y_continuous(breaks=seq(0.3,1.25,0.25),limits=c(0.3,1.25))+
#  scale_x_continuous(breaks=seq(0.2,0,0.05))+
#And now we flip the axes so that SE is on y- and Zr is on x-
  coord_flip()+
#Finally, apply my APA-format theme (see code at end of post).
#You could, alternatively, specify theme_bw() instead.
  theme_bw()
print(fp)
```

@@

# select regression studies with r2
tmp <- dplyr::filter(R_summary,dimension=="arousal")
tmp <- dplyr::filter(R_studies,dimension=="arousal")
dim(tmp)
tmp <- tmp[!is.na(tmp$values),]
dim(tmp)
#tmp<-drop_na(tmp)

m.cor <- metacor(cor = values, 
                 n = stimulus_n,
                 studlab = unique_id,
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 backtransf = TRUE,
                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Arousal: Summary")

print(m.cor)
```
### Trimmed analysis
```{r}
O <- find.outliers(m.cor)
```

### 2024-07-11 analysis/preprocessing.qmd
working on preprocessing and analysis

```{r}
#C_studies$dimension[str_detect(R_studies$dimension,'activation|energy arousal|tension arousal')]<-'arousal'
#R_studies$dimension[str_detect(R_studies$dimension,'pleasantness')]<-'valence'
#R_studies <- dplyr::filter(R_studies,!str_detect(dimension,'av')) # relates to distances, can be omitted

table(C_studies$stimulus_n)

>>>>

```{r}
table(C_studies$stimulus_n)

### 2024-07-11 manuscript/manuscript.qmd
working on preprocessing and analysis

| Concept     | Models, obs|$r$ [95%-CI]              | $t$ | $p$  |$\tau^2$|$I^2$|
|:------------|:----------|:--------|:--------------|:----|:-----|:-----|:------|
| Valence All | 49,42648  | 0.6137 [0.5540; 0.6672] | 15.9|.0001 | 0.092| 98.1% |
| Valence Trim| 27,18402  | 0.6048 [0.5920; 0.6172] | 72.4|.0001 | 0.0007| 33.1% [0.0%; 58.2%]|
| Valence M   | 14,10641  | 0.6038 [0.4671; 0.7124] | 7.83|.0001 | 0.100| 97.8% |
| Valence Md  | 14,10641  | 0.6018 [0.4659; 0.7099] | 7.87|.0001 | 0.098| 97.7% |
| Valence Max | 14,10641  | 0.6520 [0.5026; 0.7636] | 7.44|.0001 | 0.142| 97.9% |
| *N Features*|           |                         |     |      |      |       |
| <18 F       |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| 18-260 F    |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| 260+ F      |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| *Techniques*|           |                         |     |      |      |       |
|   KS        |           | 0.3606 [0.3201; 0.3997] | xxxx|.xxxx | 0.xxx| XXXX% |
|   LM        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   FD        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   NN        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   RF        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |

@@

| Concept     | Models, obs|$r$ [95%-CI]             | $t$ | $p$  |$\tau^2$|$I^2$|
|:------------|:-----------|:---------|:-------------|:----|:-----|:-----|:------|
| Arousal     | 14,9035    |          |              |     |      |      |       |
| Arousal Trim| 27,18402   |          |              |     |      |      |       |
| Arousal M   | 14,10641   |          |              |     |      |      |       |
| Arousal Md  | 14,10641   |          |              |     |      |      |       |
| Arousal Max | 14,10641   |          |              |     |      |      |       |
| *N Features*|            |          |              |     |      |      |       |   
| <18 F       |            |          |              |     |      |      |       |
| 18-260 F    |            |          |              |     |      |      |       |
| 260+ F      |            |          |              |     |      |      |       |
| *Techniques*|            |          |              |     |      |      |       |  
|   KS        |            |          |              |     |      |      |       |
|   LM        |            |          |              |     |      |      |       |
|   FD        |            |          |              |     |      |      |       |
|   NN        |            |          |              |     |      |      |       |
|   RF        |            |          |              |     |      |      |       |

>>>>

| Concept     | Models, obs|$r$ [95%-CI]            | $t$ | $p$  |$\tau^2$|$I^2$|
|:------------|:----------|:--------  --------------|:----|:-----|:-----|:------|
| Valence All | 49,42480  | 0.6137 [0.5540; 0.6672] | 15.9|.0001 | 0.092| 98.1% |
| Valence Trim| 27,18402  | 0.6048 [0.5920; 0.6172] | 72.4|.0001 | 0.0007| 33.1%|
| Valence M   | 14,10641  | 0.6038 [0.4671; 0.7124] | 7.83|.0001 | 0.100| 97.8% |
| Valence Md  | 14,10641  | 0.6018 [0.4659; 0.7099] | 7.87|.0001 | 0.098| 97.7% |
| Valence Max | 14,10641  | 0.6520 [0.5026; 0.7636] | 7.44|.0001 | 0.142| 97.9% |
| Val. MaxTrim|   8,7205  | 0.6140 [0.5538; 0.6679] | 18.5|.0001 | 0.008| 88.5% |
| *N Features*|           |                         |     |      |      |       |
| <18 F       |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| 18-260 F    |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| 260+ F      |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| *Techniques*|           |                         |     |      |      |       |
|   KS        |           | 0.3606 [0.3201; 0.3997] | xxxx|.xxxx | 0.xxx| XXXX% |
|   LM        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   FD        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   NN        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   RF        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |

@@

| Concept     | Models, obs|$r$ [95%-CI]             | $t$ | $p$  |$\tau^2$|$I^2$|
|:------------|:-----------|:------------------------|:----|:-----|:-----|:------|
| Arousal     | 55,43160   | 0.7959 [0.7666; 0.8218] |29.0 |0.0001|0.0676|95.6%  |
| Arousal Trim| 27,18402   | 0.7932 [0.7846; 0.8014] | 96.5|0.0001|0.0030|73.3%  |
| Arousal M   | 14,10641   | 0.7567 [0.6752; 0.8199] | 12.7|0.0001|0.0739|95.6%  |
| Arousal Md  | 14,10641   | 0.7627 [0.6819; 0.8252] | 12.7|0.0001|0.0757|95.3%  |
| Arousal Max | 14,10641   | 0.8077 [0.7088; 0.8755] | 10.3|0.0001|0.155 | 96.8%  |
| Aro.Max.Trm | 11,10021   | 0.7869 [0.7490; 0.8197] | 25.6|0.0001|0.0132| 96.8%  |

| *N Features*|            |          |              |     |      |      |       |   
| <18 F       |            |          |              |     |      |      |       |
| 18-260 F    |            |          |              |     |      |      |       |
| 260+ F      |            |          |              |     |      |      |       |
| *Techniques*|            |          |              |     |      |      |       |  
|   KS        |            |          |              |     |      |      |       |
|   LM        |            |          |              |     |      |      |       |
|   FD        |            |          |              |     |      |      |       |
|   NN        |            |          |              |     |      |      |       |
|   RF        |            |          |              |     |      |      |       |
